Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
refz

Our observations add to the evidence that caribou can, and occasionally do, swim
in the ocean (Table 1). While past observations (e.g. @Miller_1995;
@Jeffrey_2007; @Ricca_2012] have noted the exceptional nature of caribou
swimming in the ocean, we suggest that this behaviour is likely more common than
previously thought for caribou living on oceanic islands. We posit forage
limitation and the associated density-dependent habitat selection is an ultimate
explanation for why caribou swimming in the ocean, with predator avoidance as a
potential proximate explanation. Although our inference is limited to
observations, our observations suggest that islands represent discrete foraging
patches for terrestrial animals that could influence fitness via increased
foraging opportunities and safety from predators. We also suggest that
individuals vary in their evaluation of costs and benefits of movement between
these habitat patches.

>>>>

Our observations add to the evidence that caribou can, and occasionally do, swim
in the ocean (Table 1). While past observations (e.g.
@Jeffery_2007; @Ricca_2012] <!-- add Miller 1995, Miller 2002 --> have noted the
exceptional nature of caribou swimming in the ocean, we suggest that this
behaviour is likely more common than previously thought for caribou living on
oceanic islands. We posit forage limitation and the associated density-dependent
habitat selection is an ultimate explanation for why caribou swimming in the
ocean, with predator avoidance as a potential proximate explanation. Although
our inference is limited to observations, our observations suggest that islands
represent discrete foraging patches for terrestrial animals that could influence
fitness via increased foraging opportunities and safety from predators. We also
suggest that individuals vary in their evaluation of costs and benefits of
movement between these habitat patches.
